\include{resume-include}
\usepackage[english]{babel}

\begin{document}
\pagestyle{empty}

\header{
		\mycolor{contact}\\
		272 \textsc{Cours Lafayette} \\
		69003 \textsc{Lyon FRANCE}\\~\\
		+33 (0) 6 84 88 87 05\\
		etienne.brodu@insa-lyon.fr
	}
	{
		\textsc{Etienne}\\
		\textsc{Brodu}
	}
	{
		\textsc{Software developer}\\
		\textsc{UI/UX Designer}
	}
	
	
	
\section{Education}
	\subsection{2007 - 2012}
		{Master of Engineering in Computer Sciences and Information Technology, National Institute of Applied Sciences (INSA) of Lyon, France}
		
	\subsection{2004 - 2007}
		{Advanced Scientific High School Diploma passed with honors Lyc\'{e}e Jean Moulin, Angers, France. Specialization: Engineering Sciences}

\section{Work Experiences}
	\subsection{June - August 2010}
		{Third year Internship: In the CITI laboratory (INRIA), working on android's virtual machine dalvik to adapt to an OSGi modification. Used Java and C/C++ with JNI.}

	\subsection{2009}
		{Second year Project: An accurate gravitational model. Language used : OpenGL.}
		
	\subsection{2008}
		{Website for the Insa Ski club. Languages used: Javascript/ HTML/ CSS.}
				
	\subsection{2006}
		{High School Project: Clock using the retinal persistence.\\
		 Microcontroller code in C.\\
		 Jury presentation.}
		
\section{Special Skills}
	\subsection{Programming languages}
		{UML, C, C++, Java, Assembler 68K and x86, Oracle, SQL, PL/SQL, XML, (X)HTML, CSS, \LaTeX, Prolog, Starlet, Matlab}
		
	\subsection{Operating systems}
		{GNU Linux (Gentoo, Debian-like ...), Mac os X, Microsoft Windows, VxWorks}
		
	\subsection{Networks}
		{Network architecture, Internet architecture, ISO architecture, fixed and mobile telecommunications, networks administration and security, Network functions, data links, IP, local Area Networks}

	\subsection{Design methods}
		{MERISE, UML, SART, USDP, ERP}
		
	\subsection{Tools \& Library}
		{Android, Qt, XCode, Eclipse, NetBeans, Matlab, Rational Softare Architect}
		
	\subsection{Languages}
		{French (native),\\English (fluent),\\German(Beginner)}
				
\section{Miscellaneous}
	\subsection{Travel}
		{In Scandinavia, Germany, England, Ireland, Baltic States, Italia. Many experiences of live in a commune during those travels}
		
	\subsection{Associations activities}
		{BdE de l'Insa de Lyon (Student Union), free student-organized festival "\textit{les 24h de l'Insa de Lyon}" ...)}
		
	\subsection{Activities}
		{Graphic design : Adobe Creative Suite ( Photoshop, Illustrator, InDesign ... ),\\Camp counselor.}
		
	\subsection{Sport}
		{Climbing, snowboarding, running ...}
		
\end{document}
